\section{Multimodal fusion}
\label{sec:multimodal}

As names are propagated based on the outputs of face and speech processing modules independently in CBN and VBN systems, 
we employed a fusion strategy to aggregate the results. 
Meanwhile, it is more straightforward to combine 2 modalities as joint similarity in GBN.

\mypartitle{Late fusion ranking.} 
Within each shot, $\{N^F_i, f(N^F_i)\}$ is the set of names returned by face naming and the corresponding talking scores and $\{N^A_i,  s(N^A_i)\}$  is the set of names returned by speaker naming.
%
The final set is the union of ${N^F_i}$ and ${N^A_i}$. The names which the two methods agree on are ranked highest.
%
The same late fusion strategy is applied to both CBN and VBN but with different ranking strategies.
%
For the disjoint names, VBN systems ranks them based on the scores. 
Meanwhile, for CBN names from talking face naming are ranked higher than speaker naming 
because we found that face naming is more reliable in empirical experiments.
%
%Alternative strategies that rank speaker naming equal or higher than face naming gave inferior results.
%
%The same late fusion strategy is applied to both clustering-based naming and verification-based naming.

\mypartitle{Audiovisual similarity.} For the graph-based approach, the audio and visual modalities can be combined straightforwardly into one similarity.
%
Thus the similarity is extended to multi-modality by using a linear combination of the audio and visual similarities defined in section \ref{ssec:graph_gen}: $\sigma^{AV}_{ij} = \beta \sigma^V_{ij} + (1-\beta) \sigma^A_{ij}$. $\beta$ is experimentally set to 0.5.

\endinput

\begin{algorithm}
  \caption{Ranking names within shots
    \label{algo:ranking}}
  \begin{algorithmic}[1]
	  \For{$s_k \in S$}
 	  	    \State{$Q_{s_k} = \emptyset$}
		    \State{Face\_naming$(s_k) \Rightarrow (N^F_i, t(N^F_i))$}
				\State{Speaker\_naming$(s_k) \Rightarrow (N^A_j, 1.0)$}
				\For{each $N^F_i$}
					\If{$\exists N^A_j / N^A_j = N^F_i$}
						\State{$Q_{s_k} = Q_{s_k} \cup \{(N^F_i, t(N^F_i) + 2.0)\}$}
					\Else
						\State{$Q_{s_k} = Q_{s_k} \cup \{(N^F_i, t(N^F_i) + 1.0)\}$}
					\EndIf
				\EndFor
				\For{each $N^A_j$}
					\If{not $\exists N^F_i / N^F_i = N^A_j$}
						\State{$Q_{s_k} = Q_{s_k} \cup \{(N^A_j, 1.0)\}$}
					\EndIf
				\EndFor
		\EndFor
  \end{algorithmic}
\end{algorithm}
%
