\section{Name initialization and verification}
\label{sec:verification}


The proposed system can be divided in an enrolment and a search stage. For each person name detected by optical character recognition (OCR), the most likely interval
of speech and face presence are detected and used for enrolment.
%, as depicted in Figure \ref{fig:timeline}. 
Once the detected people are enrolled, speaker and face recognition
are performed for each shot in order to assign labels to that shot. 
A decision fusion strategy is implemented in order to combine the speech and video labels. The details of the system
are described below.

\subsection{Enrollment}

\subsubsection{GTM-UVigo system}
First, audio and video features were extracted from the recordings. The audio features were 19 MFCCs plus delta, acceleration and energy. For the video features, first
the baseline face tracking approach was used to detect faces, and then discrete cosine transform (DCT) features \cite{mccool2009} were extracted using blocks of size 12
with 50\% overlap and 45 DCT comonents using the Bob toolkit \cite{bob2012}, preceeded by geometric normalization and photometric enhancement using the Tan\&Triggs algorithm
\cite{tan2010}.

For each person name detected by the OCR, the intervals of voice activity detection and appearance of that person were extracted. For the audio, 
the time interval $(t_{\mathrm{start}},t_{\mathrm{end}})$ in which the name of the speaker $spk$ appears is taken as a starting point. A strategy to enlarge this time
 interval in order to obtain more data to enrol the speaker is applied: given the time intervals $S_{\mathrm{left}} = (t_{\mathrm{start}}-10,t_{\mathrm{end}})$ and 
 $S_{\mathrm{right}} = (t_{\mathrm{start}},t_{\mathrm{end}}+10)$, a change point is searched within each of these intervals using the Bayesian information criterion algorithm
 (BIC) for speaker segmentation,  having the restriction that the change point has to be in the 
 intervals $(t_{\mathrm{start}}-10,t_{\mathrm{start}})$ and $(t_{\mathrm{end}},t_{\mathrm{end}}+10)$, respectively. If no change point was found within the interval
 $S_{\mathrm{left}}$ then $t_{\mathrm{left}}$ is set to $t_{\mathrm{start}}-10$ and, similarly, if no change point was found within the interval 
 $S_{\mathrm{right}}$ then $t_{\mathrm{right}}$ is set to $t_{\mathrm{end}}+10$. Then, speaker $spk$ is assumed to be speaking in the interval 
 $S_{\mathrm{spk}} = (t_{\mathrm{left}},t_{\mathrm{right}})$. For the video, the faces detected by the face tracker in the interval $(t_{\mathrm{start}},t_{\mathrm{end}})$ in 
 which the name of the speaker $spk$ appears were considered; given that only one face was detected, the whole presence interval of that face is taken but, in case more than 
 one face was detected, the one that appeared in more frames was assigned to the speaker, assuming that was the dominant face in the given time interval.
 In case the person appears several times in the OCR output, a segment is computed for each occurrence.
 
 Finally, once the intervals of appearance are defined, an i-vector \cite{dehak10} is extracted for each modality using Kaldi toolkit \cite{kaldi}; in the case of speech, speech activity detection (SAD) was performed
 beforehand, in order to remove the non-speech intervals. In case several segments were available for a person name, their features were concatenated and all the segments
 were treated as a single one.

\subsection{Search}

\subsubsection{GTM-UVigo system}

In order to decide which speaker was present in a shot, first speech and face detection were performed. Speech detection was carried out using a logistic regression approach
used to classify a segment as speech or non-speech, discarding the non-speech segments. For the video, the faces detected by the face tracker within the shot were identified, 
and the one that appeared in more frames (if any) was chosen. Afther that, the same procedure as in the enrollment stage was performed: features were extracted from the shot
and an i-vector was extracted for each modality (in the case of speech, this was preceeded by speech activity detection). Once the i-vectors of the shot were obtained,
cosine scoring with the enrollment i-vectors was computed, choosing the person names that achieved the highest score for each modality. The shot was assigned to
a person if the name assigned by the face and
speech modalities were equal and the sum of their scores were greater than a threshold.

\endinput